Simultaneous segmentation and distortion correction on diffusion weighted MR using shape priors

### 2012-12-12 Publications/2013-IPMI/Latex/00-Main.tex
fixed affiliation

\usepackage[hyphens]{url}
\usepackage{nameref}
\usepackage[breaklinks]{hyperref}
\usepackage[USenglish]{babel}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{pslatex}
%

@@

\usepackage{graphicx}

%
%\tableofcontents
%
\mainmatter              % start of the contributions
%
\graphicspath{{../Figures/}}

@@

\title{Simultaneous segmentation and distortion correction on diffusion weighted MR using shape priors}
%%
\titlerunning{Segmentation & EPI correction on DWI}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Oscar Esteban\inst{1,2} \and Alessandro Daducci \inst{2} \and
		Meritxell Bach-Cuadra \inst{2} \and Virginia Estellers \inst{2}
		\and Mar\'ia-Jes\'us Ledesma-Carbayo \and Luminita Vese \inst{3} \and 
        Jean-Philippe Thiran \inst{2} \and Andr\'es Santos \inst{1} \and
        Dominique Zosso \inst{2,3}}
%
\authorrunning{Oscar Esteban et al.} % abbreviated author list (for running head)

\institute{Biomedical Image Technologies (BIT),
ETSI Telecomunicaci\'on - Universidad Polit\'ecnica de Madrid
and CIBER-BBN, \\
Av. Complutense 30, E-28040 Madrid, Spain\\
\email{oscar.esteban@upm.es},\\
% WWW home page:
%\texttt{http://users/\homedir iekeland/web/welcome.html}
\and
Signal Processing Laboratory 5 (LTS5),
\'Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL)\\
EPFL-STI-IEL-LTS5, Station 11, CH-1015 Lausanne, Switzerland
\and
Department of Mathematics, ... 
University of California Los Angeles (UCLA),
Los Angeles,..
}

>>>>

\usepackage[hyphens]{url}
\usepackage{nameref}
\usepackage{hyperref}
\usepackage[USenglish]{babel}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{pslatex}
%

@@

%
%\tableofcontents
%
\mainmatter              % start of the contributions
%

@@

\title{Simultaneous segmentation and distortion correction on diffusion weighted MR using shape priors}
%%
\titlerunning{Segmentation & EPI correction on DWI}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Oscar Esteban\inst{1,2} \and Alessandro Daducci \inst{2} \and
        Jean-Philippe Thiran \inst{2} \and Andr\'es Santos \inst{1} \and
        Dominique Zosso \inst{2,3}}
%
\authorrunning{Oscar Esteban et al.} % abbreviated author list (for running head)

\institute{Biomedical Image Technologies (BIT),
ETSI Telecomunicaci\'on - Universidad Polit\'ecnica de Madrid
and CIBER-BBN, \\
Av. Complutense 30, E-28040 Madrid, Spain\\
\email{oscar.esteban@upm.es},\\
% WWW home page:
%\texttt{http://users/\homedir iekeland/web/welcome.html}
\and
Signal Processing Laboratory (LTS5),
\'Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL)\\
EPFL STI IEL LTS5, Station 11, CH-1015 Lausanne, Switzerland
\and
Department of Mathematics, University of California, Los Angeles (UCLA)\\
520 Portola Plaza, Box 951555, Los Angeles, CA 90095-1555, U.S.A.
}
